---
title: "Hemp Phyloseq Analysis for Manuscript"
author: "Jaime Blair"
date: "2025-06-05"
output: html_document
---

##Load Libraries
```{r}
#if (!requireNamespace("BiocManager", quietly = TRUE))
#    install.packages("BiocManager")
#BiocManager::install("dada2", version = "3.17")
library(dada2)

#install.packages("tidyverse")
library(tidyverse)

#BiocManager::install("phyloseq")
library(phyloseq)  

#install.packages("ggforce")
library(ggforce)

#install.packages("htmltools")
library(htmltools)

#install.packages("vegan")
library(vegan)

#install.packages("dplyr")
library(dplyr)

#install.packages("viridis") 
library(viridis)

library(tibble)

#BiocManager::install("DECIPHER")
#library(DECIPHER)
#BiocManager::install("Biostrings")
#library(Biostrings)


```

## Load DADA2 files to create Phyloseq Objects
For rps10: some eDNA samples failed to amplify. Empty columns were added to RevisedOTU_counts so all samples and locations could be graphed together.
```{r}
# Read counts and taxa tables into new variables for each locus
COIcount_df <- read.table("COI_RevisedOTU_counts.tsv", header=T, row.names=1, check.names=F, sep="\t")
COItaxa_df <- as.matrix(read.csv("COI_RevisedOTU_taxa.tsv", header=T, row.names=1, check.names=F, sep="\t"))

RPScount_df <- read.table("rps10_RevisedOTU_counts.tsv", header=T, row.names=1, check.names=F, sep="\t")
RPStaxa_df <- as.matrix(read.csv("rps10_RevisedOTU_taxa.tsv", header=T, row.names=1, check.names=F, sep="\t"))

ITScount_df <- read.table("ITS_RevisedOTU_counts.tsv", header=T, row.names=1, check.names=F, sep="\t")
ITStaxa_df <- as.matrix(read.csv("ITS_RevisedOTU_taxa.tsv", header=T, row.names=1, check.names=F, sep="\t"))

# Read in metadata file
COImetadata <- read.csv("COI_metadata.csv")
RPSmetadata <- read.csv("rps10_metadata.csv")
ITSmetadata <- read.csv("ITS_metadata.csv")

# Make the sample names the row names for sample information
COImetadata <- COImetadata %>% remove_rownames %>% column_to_rownames(var="SampleName")
COImetadata <- as.data.frame(COImetadata)
RPSmetadata <- RPSmetadata %>% remove_rownames %>% column_to_rownames(var="SampleName")
RPSmetadata <- as.data.frame(RPSmetadata)
ITSmetadata <- ITSmetadata %>% remove_rownames %>% column_to_rownames(var="SampleName")
ITSmetadata <- as.data.frame(ITSmetadata)

# Transform data into phyloseq object
COIsample_info_tab_phy <- sample_data(COImetadata)
COIcount_tab_phy <- otu_table(COIcount_df, taxa_are_rows=T) 
COItax_tab_phy <- tax_table(COItaxa_df)

COIPhyloseq_object <- phyloseq(COIcount_tab_phy,
                            COItax_tab_phy,
                            COIsample_info_tab_phy)
COIPhyloseq_object #Print phyloseq summary

RPSsample_info_tab_phy <- sample_data(RPSmetadata)
RPScount_tab_phy <- otu_table(RPScount_df, taxa_are_rows=T) 
RPStax_tab_phy <- tax_table(RPStaxa_df)

RPSPhyloseq_object <- phyloseq(RPScount_tab_phy,
                            RPStax_tab_phy,
                            RPSsample_info_tab_phy)
RPSPhyloseq_object #Print phyloseq summary

ITSsample_info_tab_phy <- sample_data(ITSmetadata)
ITScount_tab_phy <- otu_table(ITScount_df, taxa_are_rows=T) 
ITStax_tab_phy <- tax_table(ITStaxa_df)

ITSPhyloseq_object <- phyloseq(ITScount_tab_phy,
                            ITStax_tab_phy,
                            ITSsample_info_tab_phy)
ITSPhyloseq_object #Print phyloseq summary

```

## Alpha Diversity (complete dataset)
```{r}
# Observed species richness across all datasets
COI_Obs <- plot_richness(COIPhyloseq_object, x="SampleID", color = "HempType", measures=c("Observed"))+ 
  geom_boxplot()+
  scale_colour_viridis_d()+
  theme_bw()+
  ylab("Species Richness")+
  theme(axis.text.x = element_text(angle = 45, hjust=1))+
  ggtitle("COI")
COI_Obs

RPS_Obs <- plot_richness(RPSPhyloseq_object, x="SampleID", color = "HempType", measures=c("Observed"))+ 
  geom_boxplot()+
  scale_colour_viridis_d()+
  theme_bw()+
  ylab("Species Richness")+
  theme(axis.text.x = element_text(angle = 45, hjust=1))+
  ggtitle("rps10")
RPS_Obs

ITS_Obs <- plot_richness(ITSPhyloseq_object, x="SampleID", color = "HempType", measures=c("Observed"))+ 
  geom_boxplot()+
  scale_colour_viridis_d()+
  theme_bw()+
  ylab("Species Richness")+
  theme(axis.text.x = element_text(angle = 45, hjust=1))+
  ggtitle("ITS")
ITS_Obs

```


## Alpha Diversity Analysis of eDNA Samples (no Mock Communities)
```{r}
# Remove mocks from dataset
COIeDNA_Phyloseq <- subset_samples(COIPhyloseq_object, HempType != "Mock")
#COIeDNA_Phyloseq

RPSeDNA_Phyloseq <- subset_samples(RPSPhyloseq_object, HempType != "Mock")
#RPSeDNA_Phyloseq

ITSeDNA_Phyloseq <- subset_samples(ITSPhyloseq_object, HempType != "Mock")
#ITSeDNA_Phyloseq

COIeDNA_Alpha <- plot_richness(COIeDNA_Phyloseq, x="Location", color = "HempType", measures=c("ACE","Shannon"))+ 
  geom_boxplot()+
  scale_colour_manual(values = c("orange", "darkgreen"))+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust=1))+
  ggtitle("COI")
COIeDNA_Alpha

RPSeDNA_Alpha <- plot_richness(RPSeDNA_Phyloseq, x="Location", color = "HempType", measures=c("ACE","Shannon"))+ 
  geom_boxplot()+
  scale_colour_manual(values = c("orange", "darkgreen"))+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust=1))+
  ggtitle("rps10")
RPSeDNA_Alpha

ITSeDNA_Alpha <- plot_richness(ITSeDNA_Phyloseq, x="Location", color = "HempType", measures=c("ACE","Shannon"))+ 
  geom_boxplot()+
  scale_colour_manual(values = c("orange", "darkgreen"))+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust=1))+
  ggtitle("ITS")
ITSeDNA_Alpha

```

## Alpha Diversity Kruskal-Wallace Tests on eDNA Samples (no Mock Communities)
Conversion function from: https://jacobrprice.github.io/2017/08/26/phyloseq-to-vegan-and-back.html
```{r}
# convert the sample_data() metadata within a phyloseq object to a vegan compatible data object
pssd2veg <- function(physeq) {
  sd <- sample_data(physeq)
  return(as(sd,"data.frame"))
}

# convert the otu_table() within a phyloseq object to a vegan compatible data object
# don't need this because PhyloSeq has estimate_richness with Phyloseq object
psotu2veg <- function(physeq) {
  OTU <- otu_table(physeq)
  if (taxa_are_rows(OTU)) {
    OTU <- t(OTU)
  }
  return(as(OTU, "matrix"))
}

COIeDNASampleFile <- pssd2veg(COIeDNA_Phyloseq)
COIeDNA_AlphaEst <- estimate_richness(COIeDNA_Phyloseq, measures = c("ACE","Shannon"))
#COIeDNA_AlphaEst
COIstats <- cbind(COIeDNASampleFile, COIeDNA_AlphaEst)
#COIstats
sink(file = "COI_KruskalOutputs.txt")
COIresult1 <- kruskal.test(Shannon ~ Location, data = COIstats)
COIresult1
COIresult2 <- kruskal.test(Shannon ~ HempType, data = COIstats)
COIresult2
COIresult3 <- kruskal.test(ACE ~ Location, data = COIstats)
COIresult3
COIresult4 <- kruskal.test(ACE ~ HempType, data = COIstats)
COIresult4
sink(file=NULL)

ITSeDNASampleFile <- pssd2veg(ITSeDNA_Phyloseq)
ITSeDNA_AlphaEst <- estimate_richness(ITSeDNA_Phyloseq, measures = c("ACE","Shannon"))
#ITSeDNA_AlphaEst
ITSstats <- cbind(ITSeDNASampleFile, ITSeDNA_AlphaEst)
#ITSstats
sink(file = "ITS_KruskalOutputs.txt")
ITSresult1 <- kruskal.test(Shannon ~ Location, data = ITSstats)
ITSresult1
ITSresult2 <- kruskal.test(Shannon ~ HempType, data = ITSstats)
ITSresult2
ITSresult3 <- kruskal.test(ACE ~ Location, data = ITSstats)
ITSresult3
ITSresult4 <- kruskal.test(ACE ~ HempType, data = ITSstats)
ITSresult4
sink(file=NULL)

FullRPS <- estimate_richness(RPSeDNA_Phyloseq, measures = "ACE")
FullRPSSampleFile <- pssd2veg(RPSeDNA_Phyloseq)
FullRPSstats <- cbind(FullRPSSampleFile, FullRPS)
sink(file = "RPS_KruskalOutputs.txt")
FullRPSresult3 <- kruskal.test(ACE ~ Location, data = FullRPSstats)
FullRPSresult3
FullRPSresult4 <- kruskal.test(ACE ~ HempType, data = FullRPSstats)
FullRPSresult4

RPSnoMiss <- subset_samples(RPSeDNA_Phyloseq, Location != "LocationC")
RPSnoMiss <- subset_samples(RPSnoMiss, Location != "LocationE")
RPSnoMiss <- subset_samples(RPSnoMiss, SampleID != "D")
RPSeDNASampleFile <- pssd2veg(RPSnoMiss)
RPSeDNA_AlphaEst <- estimate_richness(RPSnoMiss, measures = "Shannon")
#RPSeDNA_AlphaEst
RPSstats <- cbind(RPSeDNASampleFile, RPSeDNA_AlphaEst)
#RPSstats
RPSresult1 <- kruskal.test(Shannon ~ Location, data = RPSstats)
RPSresult1
RPSresult2 <- kruskal.test(Shannon ~ HempType, data = RPSstats)
RPSresult2
sink(file=NULL)


```


## Beta Diversity (complete dataset)
```{r}
# Transform to even sampling depth (convert counts to percentages)
COI_transformed = transform_sample_counts(COIPhyloseq_object, function(x) x/sum(x)*100) 

# Bray-Curtis dissimilarity index
COIdistance_bray = phyloseq::distance(COI_transformed, method = "bray")
COIordinate_PCoA_bray = ordinate(COI_transformed, method = "PCoA", distance = "COIdistance_bray")
COIPCoA_plot_bray <- plot_ordination(COI_transformed, COIordinate_PCoA_bray, color = "HempType", label = "SampleID")+
  theme_bw()+
  stat_ellipse()+ #uses a 95% confidence interval
  ggtitle("COI Bray-Curtis PCoA")
COIPCoA_plot_bray

# Jaccard dissimilarity index
COIdistance_jacc = phyloseq::distance(COI_transformed, method = "jaccard", binary=TRUE)
COIordinate_PCoA_jacc = ordinate(COI_transformed, method = "PCoA", distance = "COIdistance_jacc")
COIPCoA_plot_jacc <- plot_ordination(COI_transformed, COIordinate_PCoA_jacc, color = "HempType", label = "SampleID")+
  theme_bw()+
  stat_ellipse()+ #uses a 95% confidence interval
  ggtitle("COI Jaccard PCoA")
COIPCoA_plot_jacc
```

## Beta Diversity Analysis of eDNA Samples (no Mock Communities)
```{r}
# Remove mocks from dataset
#COIeDNA_Phyloseq <- subset_samples(COIPhyloseq_object, HempType != "Mock")
#COIeDNA_Phyloseq
#RPSeDNA_Phyloseq <- subset_samples(RPSPhyloseq_object, HempType != "Mock")
#RPSeDNA_Phyloseq
#ITSeDNA_Phyloseq <- subset_samples(ITSPhyloseq_object, HempType != "Mock")
#ITSeDNA_Phyloseq

# Transform to even sampling depth (convert counts to percentages)
COIeDNA_transformed = transform_sample_counts(COIeDNA_Phyloseq, function(x) x/sum(x)*100)
RPSeDNA_transformed = transform_sample_counts(RPSnoMiss, function(x) x/sum(x)*100)
ITSeDNA_transformed = transform_sample_counts(ITSeDNA_Phyloseq, function(x) x/sum(x)*100)

# Jaccard dissimilarity index
COIeDNA_jacc = phyloseq::distance(COIeDNA_transformed, method = "jaccard", binary=TRUE)
COIeDNAordinate_jacc = ordinate(COIeDNA_transformed, method = "PCoA", distance = "COIeDNA_jacc")
COIeDNAPCoA_jacc <- plot_ordination(COIeDNA_transformed, COIeDNAordinate_jacc, color = "HempType")+
  theme_bw()+
  scale_colour_manual(values = c("orange", "darkgreen"))+
  geom_text(mapping = aes(label = SampleID), size = 3, vjust = 1, nudge_y = -0.02)+
  geom_point(size=2)+
  stat_ellipse()+ #uses a 95% confidence interval
  ggtitle("COI Jaccard")
COIeDNAPCoA_jacc

RPSeDNA_jacc = phyloseq::distance(RPSeDNA_transformed, method = "jaccard", binary=TRUE)
RPSeDNAordinate_jacc = ordinate(RPSeDNA_transformed, method = "PCoA", distance = "RPSeDNA_jacc")
RPSeDNAPCoA_jacc <- plot_ordination(RPSeDNA_transformed, RPSeDNAordinate_jacc, color = "HempType")+
  theme_bw()+
  scale_colour_manual(values = c("orange", "darkgreen"))+
  geom_text(mapping = aes(label = SampleID), size = 3, vjust = 1, nudge_y = -0.02)+
  geom_point(size=2)+
  stat_ellipse()+ #uses a 95% confidence interval
  ggtitle("rps10 Jaccard")
RPSeDNAPCoA_jacc

ITSeDNA_jacc = phyloseq::distance(ITSeDNA_transformed, method = "jaccard", binary=TRUE)
ITSeDNAordinate_jacc = ordinate(ITSeDNA_transformed, method = "PCoA", distance = "ITSeDNA_jacc")
ITSeDNAPCoA_jacc <- plot_ordination(ITSeDNA_transformed, ITSeDNAordinate_jacc, color = "HempType")+
  theme_bw()+
  scale_colour_manual(values = c("orange", "darkgreen"))+
  geom_text(mapping = aes(label = SampleID), size = 3, vjust = 1, nudge_y = -0.02)+
  geom_point(size=2)+
  stat_ellipse()+ #uses a 95% confidence interval
  ggtitle("ITS Jaccard")
ITSeDNAPCoA_jacc

```

## PERMANOVA
From: https://github.com/joey711/phyloseq/issues/689
```{r}
#library(vegan)
sink(file = "PermanoveOut.txt")
COImetadata <- as(sample_data(COIeDNA_transformed), "data.frame")
adonis2(distance(COIeDNA_transformed, method="jaccard") ~ HempType, data = COImetadata)
adonis2(distance(COIeDNA_transformed, method="jaccard") ~ Location, data = COImetadata)

ITSmetadata <- as(sample_data(ITSeDNA_transformed), "data.frame")
adonis2(distance(ITSeDNA_transformed, method="jaccard") ~ HempType, data = ITSmetadata)
adonis2(distance(ITSeDNA_transformed, method="jaccard") ~ Location, data = ITSmetadata)

RPSmetadata <- as(sample_data(RPSeDNA_transformed), "data.frame")
adonis2(distance(RPSeDNA_transformed, method="jaccard") ~ HempType, data = RPSmetadata)
adonis2(distance(RPSeDNA_transformed, method="jaccard") ~ Location, data = RPSmetadata)
sink(file=NULL)


```

## Relative Abundance Plots for eDNA Samples (no Mock Communities)
```{r}
# Remove mocks from dataset
#COIeDNA_Phyloseq <- subset_samples(COIPhyloseq_object, HempType != "Mock")
#COIeDNA_Phyloseq
#RPSeDNA_Phyloseq <- subset_samples(RPSPhyloseq_object, HempType != "Mock")
#RPSeDNA_Phyloseq
#ITSeDNA_Phyloseq <- subset_samples(ITSPhyloseq_object, HempType != "Mock")
#ITSeDNA_Phyloseq

# Merge OTUs of the same species
COI.glom = tax_glom(COIeDNA_Phyloseq, taxrank = "Species")
# Merge by location
COIlocations.glom = merge_samples(COI.glom, "Location", fun=sum) 
COIlocations.glom.df = psmelt(COIlocations.glom)
write_excel_csv(COIlocations.glom.df, "COImergedSpeciesLocations.xls")
  
RPS.glom = tax_glom(RPSnoMiss, taxrank = "Species")
RPSlocations.glom = merge_samples(RPS.glom, "Location", fun=sum) 
RPSlocations.glom.df = psmelt(RPSlocations.glom)
write_excel_csv(RPSlocations.glom.df, "RPSmergedSpeciesLocations.xls")

ITS.glom = tax_glom(ITSeDNA_Phyloseq, taxrank = "Species")
ITSlocations.glom = merge_samples(ITS.glom, "Location", fun=sum) 
ITSlocations.glom.df = psmelt(ITSlocations.glom)
write_excel_csv(ITSlocations.glom.df, "ITSmergedSpeciesLocations.xls")

# Create list of top 10 OTUs in COI
top10 <- names(sort(taxa_sums(COI.glom), decreasing = TRUE)[1:10])
top10
# Prune out all taxa except those top 10
prune.top10 = prune_taxa(top10, COI.glom)
ntaxa(prune.top10) #this should return 10
# Normalize the top 10 taxa to be out of 100
COI.trans = transform_sample_counts(prune.top10, function(x) x/sum(x)*100)
# Create a dataframe that has melted the normalized relative abundances of the top 10 taxa
COI.dataframe = psmelt(COI.trans)

COItop10 <- ggplot(COI.dataframe, aes(x=SampleID, y=Abundance, fill=Species))+
  theme_classic()+
  geom_bar(stat="identity")+
  scale_fill_hue(l=55)+
  xlab("SampleID")+
  ylab("Relative Abundance %")+
  labs(fill = "Top 10 Species")+
  ggtitle("Relative Abundance of Oomycete Species: COI barcode")+
  theme(axis.text.x = element_text(angle = 45, hjust=1)) #+
  #facet_wrap(~Location)
COItop10

# Create list of top 10 OTUs in RPS
Rtop10 <- names(sort(taxa_sums(RPS.glom), decreasing = TRUE)[1:10])
Rtop10
# Prune out all taxa except those top 10
prune.Rtop10 = prune_taxa(Rtop10, RPS.glom)
ntaxa(prune.Rtop10) #this should return 10
# Normalize the top 10 taxa to be out of 100
RPS.trans = transform_sample_counts(prune.Rtop10, function(x) x/sum(x)*100)
# Create a dataframe that has melted the normalized relative abundances of the top 10 taxa
RPS.dataframe = psmelt(RPS.trans)

RPStop10 <- ggplot(RPS.dataframe, aes(x=SampleID, y=Abundance, fill=Species))+
  theme_classic()+
  geom_bar(stat="identity")+
  scale_fill_hue(l=55)+
  xlab("SampleID")+
  ylab("Relative Abundance %")+
  labs(fill = "Top 10 Species")+
  ggtitle("Relative Abundance of Oomycete Species: rps10 barcode")+
  theme(axis.text.x = element_text(angle = 45, hjust=1)) #+
  #facet_wrap(~Location)
RPStop10

# Create list of top 10 OTUs in ITS
Itop10 <- names(sort(taxa_sums(ITS.glom), decreasing = TRUE)[1:10])
Itop10
# Prune out all taxa except those top 10
prune.Itop10 = prune_taxa(Itop10, ITS.glom)
ntaxa(prune.Itop10) #this should return 10
# Normalize the top 10 taxa to be out of 100
ITS.trans = transform_sample_counts(prune.Itop10, function(x) x/sum(x)*100)
# Create a dataframe that has melted the normalized relative abundances of the top 10 taxa
ITS.dataframe = psmelt(ITS.trans)

ITStop10 <- ggplot(ITS.dataframe, aes(x=SampleID, y=Abundance, fill=Species))+
  theme_classic()+
  geom_bar(stat="identity")+
  scale_fill_hue(l=55)+
  xlab("SampleID")+
  ylab("Relative Abundance %")+
  labs(fill = "Top 10 Species")+
  ggtitle("Relative Abundance of Oomycete Species: ITS barcode")+
  theme(axis.text.x = element_text(angle = 45, hjust=1)) #+
  #facet_wrap(~Location)
ITStop10


```

## Heatmaps of Top 10 Abundant Taxa in eDNA Samples (no Mock Communities)
```{r}
COItaxa10 <- c("OTU2878", "OTU2418", "OTU2666", "OTU2962", "OTU2734", "OTU2665", "OTU2759", "OTU2151", "OTU1896", "OTU2857") #labels run from bottom up, so OTU at the top of the heatmap should be last on the list
COItop10HeatMap <- plot_heatmap(prune.top10, sample.label = "SampleID", taxa.label = "Species", sample.order = "SampleID", taxa.order = COItaxa10, na.value = "white", high = "#274e13", low = "#efffe9", title = "COI (93% of reads)")+
  theme(axis.text.x.bottom = element_text(angle = 45, hjust=0.5))+
  theme(axis.text.y = element_text(size=10))
COItop10HeatMap

RPStaxa10 <- c("OTU90", "OTU418", "OTU63", "OTU136", "OTU89", "OTU12", "OTU226", "OTU52", "OTU45", "OTU44")
RPStop10HeatMap <- plot_heatmap(prune.Rtop10, sample.label = "SampleID", taxa.label = "Species", sample.order = "SampleID", taxa.order = RPStaxa10, na.value = "white", high = "#274e13", low = "#efffe9", title = "rps10 (97% of reads)")+
  theme(axis.text.x.bottom = element_text(angle = 45, hjust=0.5))+
  theme(axis.text.y = element_text(size=10))
RPStop10HeatMap

ITStaxa10 <- c("OTU922", "OTU973", "OTU510", "OTU66", "OTU18", "OTU877", "OTU644", "OTU112", "OTU676", "OTU654")
ITStop10HeatMap <- plot_heatmap(prune.Itop10, sample.label = "SampleID", taxa.label = "Species", sample.order = "SampleID", taxa.order = ITStaxa10, na.value = "white", high = "#274e13", low = "#efffe9", title = "ITS (87.6% of reads)")+
  theme(axis.text.x.bottom = element_text(angle = 45, hjust=0.5))+
  theme(axis.text.y = element_text(size=10))
ITStop10HeatMap
```

## Species Abundance for Mock Communities Only
```{r}
COIMocks_Phyloseq <- subset_samples(COIPhyloseq_object, HempType == "Mock")
#COIMocks_Phyloseq

# Merge OTUs of the same species
COIMocks.glom = tax_glom(COIMocks_Phyloseq, taxrank = "Species")
# Merge by location
COIMockslocations.glom = merge_samples(COIMocks.glom, "Location", fun=sum) 
COIMockslocations.glom.df = psmelt(COIMockslocations.glom)
write_excel_csv(COIMockslocations.glom.df, "COIMocks_mergedSpeciesLocations.xls")

RPSMocks_Phyloseq <- subset_samples(RPSPhyloseq_object, HempType == "Mock")
RPSMocks_Phyloseq
RPSMocks.glom = tax_glom(RPSMocks_Phyloseq, taxrank = "Species")
RPSMockslocations.glom = merge_samples(RPSMocks.glom, "Location", fun=sum) 
RPSMockslocations.glom.df = psmelt(RPSMockslocations.glom)
write_excel_csv(RPSMockslocations.glom.df, "RPSMocks_mergedSpeciesLocations.xls")

ITSMocks_Phyloseq <- subset_samples(ITSPhyloseq_object, HempType == "Mock")
ITSMocks_Phyloseq
ITSMocks.glom = tax_glom(ITSMocks_Phyloseq, taxrank = "Species")
ITSMockslocations.glom = merge_samples(ITSMocks.glom, "Location", fun=sum) 
ITSMockslocations.glom.df = psmelt(ITSMockslocations.glom)
write_excel_csv(ITSMockslocations.glom.df, "ITSMocks_mergedSpeciesLocations.xls")

```


